Measurement and Probability in Fuzzy Quantum Theories

### 2017-07-16 prop_iop.tex
prop_iop.tex \subsection{Classical and Quantum Probability Measures} Updating...

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu:\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure~$\mu':2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}:\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu':2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then there is a density
matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$.
\end{enumerate}
\end{thm}

\begin{proof}Since case \ref{enu:sub-event-space-real-quantum2classical}
is a special case of case \ref{enu:sub-event-space-interval-quantum2classical},
it is sufficient to prove case \ref{enu:sub-event-space-interval-quantum2classical}.
Since $\events'$ is a set of mutually commuting projections, they
can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector~$P\in\events'$, its eigenvalues are $0$
or $1$. Let $\tau\left(P\right)\subseteq\Omega$ be the set of eigenvectors
whose eigenvalues are $1$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
By definition~\ref{definition:quantum-classical}, $\bar{\mu}\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
measure by lemma~\ref{lemma:classical-probability-measures}.

For case \ref{enu:sub-event-space-real-classical2quantum}, if we
pick $\rho=\sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\proj{j}$,
then $\rho$ is a density matrix because~\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\mu'\left(\left\{ j\right\} \right)\Tr\left(\proj{j}\right)=1\,.
\end{eqnarray}
Also, 
\begin{eqnarray*}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)
 =\sum_{j=1}^{N}\mu'\left(\left\{ j\right\} \right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)
 =\mu'\left(\left\{ j\right\} \right)
 =\mu'\left(\tau\left(\proj{i}\right)\right)\textrm{ for all }i\,,\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{2}\right)
 \overset{\textrm{IH}}{=}\mu'\left(\tau\left(P_{1}\right)\right)+\mu'\left(\tau\left(P_{2}\right)\right)
 =\mu'\left(\tau\left(P_{1}+P_{2}\right)\right)
\end{eqnarray*}
for commuting\nb$P_{0},P_{1}\in\events$ with $P_{0}P_{1}=\mathbb{0}$.
Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\widehat{\events}$ by induction.\end{proof}

@@

\begin{proof}Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
By theorem~\ref{thm:sub-event-space}, we can find a bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
and a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Since $\tau$ is a bijection, $\bar{\mu}'$
is convex. By theorem~\ref{thm:Shapley}, there is a classical probability
measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$ such that
\begin{eqnarray*}
 &  & \pmeas\in\mathrm{core}\left(\bar{\mu}'\right)\\
 & \Rightarrow & \pmeas\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}
\end{eqnarray*}
By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

@@

Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
By case \ref{enu:sub-event-space-real-classical2quantum} in theorem~\ref{thm:sub-event-space},
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

>>>>

\begin{thm}\label{thm:sub-event-space}Given a Hilbert space~$\Hilb$
and a mutually commuting sub-event space~$\events'\subseteq\events$,
there is a set~$\Omega$, another commuting sub-event space~$\widehat{\events}$
with $\events'\subseteq\widehat{\events}\subseteq\events$, and a
bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$ such that:
\begin{enumerate}
\item \label{enu:sub-event-space-real-quantum2classical}If $\mu':\events'\rightarrow\left[0,1\right]$
is a quantum real-valued probability measure, then there is a classical
real-valued probability measure\nb$\mu:2^{\Omega}\rightarrow\left[0,1\right]$
such that $\mu'\left(P\right)=\mu\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-interval-quantum2classical}If $\bar{\mu}':\events'\rightarrow\mathscr{I}$
is a quantum interval-valued probability measure, then there is a
classical interval-valued probability measure\nb$\bar{\mu}:2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}'\left(P\right)=\bar{\mu}\left(\tau\left(P\right)\right)$
for all $P\in\events'$.
\item \label{enu:sub-event-space-real-classical2quantum}If $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a classical real-valued probability measure, then $\mu\circ\tau:\widehat{\events}\rightarrow\left[0,1\right]$
is a QRVPM.
\item \label{enu:sub-event-space-Gleason}Given a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$,
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$.
\item $\rho$ in the previous case may not be unique.
\end{enumerate}
\end{thm}

\begin{proof}
\begin{enumerate}
\item Since this case is a special case of the next case, it is sufficient
to prove the next case. 
\item Since $\events'$ is a set of mutually commuting projections, they
can be diagonalized by a common orthonormal basis\nb$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
Pick arbitrary projector\nb$P\in\events'$, its eigenvalues are $0$
or $1$. Select its eigenvectors whose eigenvalues are $1$ into a
set\nb$\tau\left(P\right)\subseteq\Omega$. Then, we have $P=\sum_{\ket{j}\in\tau\left(P\right)}\proj{j}$,
$\widehat{\events}=\set{\sum_{\ket{j}\in E}\proj{j}}{E\subseteq\Omega}$,
and $\tau$ is a bijection between $\widehat{\events}$ and $2^{\Omega}$.
By definition\nb\ref{definition:quantum-classical}, $\bar{\mu}'\left(P\right)=\bar{\mu}^{\Omega}\left(\tau\left(P\right)\right)$,
and $\bar{\mu}^{\Omega}$ is a classical interval-valued probability
measure by lemma\nb\ref{lemma:classical-probability-measures}.
\item Trivial.
\item If we pick $\rho=\sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\proj{j}$,
then $\rho$ is a density matrix because\nb\cite{544199}
\begin{eqnarray}
\Tr\left(\rho\right) & = & \sum_{j=1}^{d}\widehat{\mu}\left(\proj{j}\right)\Tr\left(\proj{j}\right)=1\,.
\end{eqnarray}
Also, 
\begin{eqnarray}
 &  & \mu_{\rho}^{\mathrm{B}}\left(\proj{i}\right)=\sum_{j=1}^{N}\widehat{\mu}\left(\proj{j}\right)\mu_{\ket{j}}^{\mathrm{\mathrm{B}}}\left(\proj{i}\right)=\widehat{\mu}\left(\proj{i}\right)\textrm{ for all }i\,,\\
 &  & \mu_{\rho}^{\mathrm{B}}\left(P_{0}\right)+\mu_{\rho}^{\mathrm{B}}\left(P_{1}\right)\overset{\textrm{IH}}{=}\widehat{\mu}\left(P_{0}\right)+\widehat{\mu}\left(P_{1}\right)=\widehat{\mu}\left(P_{0}+P_{1}\right)
\end{eqnarray}
for orthogonal\nb$P_{0},P_{1}\in\events$. Therefore, we have $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\widehat{\mu}\left(P\right)$
for all $P\in\widehat{\events}$ by induction.
\item Consider a Hilbert space\nb$\Hilb$ of dimension 2, a mutually commuting
sub-event space~$\widehat{\events}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $,
and a QRVPM\nb$\widehat{\mu}:\widehat{\events}\rightarrow\left[0,1\right]$
such that $\widehat{\mu}\left(\proj{0}\right)=\widehat{\mu}\left(\proj{1}\right)=\frac{1}{2}$.
Then, $\proj{\ps}$ and $\proj{\minus}$ are both density matrices,
and 
\begin{eqnarray*}
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{0}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{0}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{0}\right)\,,\\
 &  & \mu_{\ket{\ps}}^{\mathrm{B}}\left(\proj{1}\right)=\mu_{\ket{\minus}}^{\mathrm{B}}\left(\proj{1}\right)=\frac{1}{2}=\widehat{\mu}\left(\proj{1}\right)\,.
\end{eqnarray*}
\end{enumerate}
\end{proof}

@@

\begin{proof}Since $\events'$ is a set of mutually commuting projections,
they can be diagonalized by a common orthonormal basis~$\Omega=\left\{ \ket{j}\right\} _{j=0}^{d-1}$.
By theorem~\ref{thm:sub-event-space}, we can find a bijection~$\tau:\widehat{\events}\rightarrow2^{\Omega}$
and a classical IVPM~$\bar{\mu}':2^{\Omega}\rightarrow\mathscr{I}$
such that $\bar{\mu}\left(P\right)=\bar{\mu}'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Since $\tau$ is a bijection, $\bar{\mu}'$
is convex. By theorem~\ref{thm:Shapley}, there is a classical probability
measure~$\pmeas:2^{\Omega}\rightarrow\left[0,1\right]$ such that
\begin{eqnarray*}
 &  & \pmeas\in\mathrm{core}\left(\bar{\mu}'\right)\\
 & \Rightarrow & \pmeas\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}\\
 & \Rightarrow & \pmeas\left(\tau\left(P\right)\right)\in\bar{\mu}\left(P\right)\textrm{ for all }P\in\widehat{\events}
\end{eqnarray*}
By theorem~\ref{thm:sub-event-space},
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}

@@

Notice that lemma~\ref{lemma:real-expectation-value-between-classical-quantum}
guarantees that for any $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$,
there exists $\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$ such that
$\mu_{\rho}^{\mathrm{B}}=\mu'\circ\tau$. On the other hand, for any
$\mu'\in\mathrm{core}\left(\bar{\mu}'\right)$, we have
\begin{eqnarray}
 &  & \mu'\left(E\right)\in\bar{\mu}'\left(E\right)\textrm{ for all }E\in2^{\Omega}\\
 & \Rightarrow & \mu'\left(\tau\left(P\right)\right)\in\bar{\mu}'\left(\tau\left(P\right)\right)=\bar{\mu}\left(P\right)\textrm{ for all }P\in\events'
\end{eqnarray}
By theorem~\ref{thm:sub-event-space},
there is a density matrix~$\rho$ such that $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\mu'\left(\tau\left(P\right)\right)$
for all $P\in\events'$. Therefore, $\mu_{\rho}^{\mathrm{B}}\in\mathrm{core}\left(\bar{\mu},\events'\right)$,
i.e., $\rho\in\coreBorn\left(\bar{\mu},\events'\right)$.\end{proof}
